Abdul Samad
Software Engineering Intern Candidate
03286008528 
abdulsamad@email.com 
GitHub 
LinkedIn
Objective
Software Engineering student with strong foundations in Data Structures, Object-Oriented Programming, and problem solv
ing. Currently exploring Machine Learning, Generative AI, and LangChain. Passionate about building scalable and efficient
real-world applications. Seeking an internship to apply and grow technical skills in a professional environment.
Education
BS Software Engineering
Information Technology University (ITU), Lahore
Technical Skills
2023– 2027
Languages:
Core Concepts:
AI / ML:
Tools & Tech:
Projects
C++, Python
Data Structures & Algorithms, Object-Oriented Programming (OOP)
Machine Learning, Generative AI, LangChain (Learning)
Docker, GitHub, GitHub Actions, KNIME, Streamlit
AI Study Assistant (PDF Chatbot)
An AI-powered chatbot that answers user queries from uploaded PDF documents.
• Developed an AI-based system for context-aware query answering from PDF documents.
Python | Streamlit | LangChain
• Implemented document parsing and response generation pipelines using Python and Streamlit.
• Exploring LangChain to enhance semantic document understanding and retrieval accuracy.
University Management System
A fully-featured desktop system to manage students, faculty, and academic operations.
• Designed and developed modules for student/faculty management, enrollment, and course handling.
• Applied OOP principles including inheritance, polymorphism, aggregation, and composition.
• Implemented attendance tracking and grading system with structured data management.
UMS Containerized Deployment
C++ | OOP
Docker | GitHub | GitHub Actions
Deployment of the University Management System in a containerized environment.
• Containerized the application using Docker for portable and consistent deployment.
• Managed version control and automated CI/CD workflows using GitHub Actions.
Rescue Line System
An optimized rescue-routing system built using core Data Structures concepts.
C++ | Data Structures & Algorithms
• Built a routing and priority system using advanced data structures for efficient problem solving.
• Focused on algorithm optimization and structured, clean data handling techniques.
Additional
• Hands-on experience with Docker and Git-based version control systems.
• Familiar with automated CI/CD pipelines using GitHub Actions.
• Actively learning and building AI-powered applications with LangChain and Streamlit.
• Strong problem-solving and analytical skills with a focus on clean, efficient code.